Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-02 manuscript.tex
overleaf update

\textcolor{red}{ The following is very rough, taken from years ago when I first started writing the manuscript }

\protect\hypertarget{..ux2fcodeux2ftest_1}{}{}

@@

The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks. Although single-photon counting is well estanblished for deep-space optical communication\textasciitilde{}\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs. However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks. The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
\textcolor{red}{Calculate reduction in power from state of the art SFP modules}

@@

\begin{itemize}
\tightlist
\item
  Efficiency = 0.84
\item
  Afterpulsing = 0 \%
\item
  Jitter = 15 ps
\item
  Deadtime = 30 ns \textcolor{red}{measure 3dB flux}
\item
  Area = 330 \(\mu m^2\)
\item
  Dark count rate = 20~Hz
\end{itemize}

@@

In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays. Recently published high-count rate arrays have figures of merit of \textcolor{red}{\(FoM_T\) for Peacoq and Resta2023 results}. This would result in a proportinal increase in the data rate.
\textcolor{red}{\(FoM_T\) for fastest InGaAs/InP gated detector}
These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
\textcolor{red}{\(FoM_T\) for DSOC array}

>>>>

{}

@@

The work here highlights the application of low jitter single-photon detectors for optical communication, which is impactful for deep-space optical communication as well as classical communication in quantum networks. Although single-photon counting is well estanblished for deep-space optical communication\textasciitilde{}\cite{Laser lunar, DSOC} so far it has not been ulitized in quantum networks, mainly due to the use of SFP modules and DWDMs. However, with the eachievement of high data rates recently achieved with photon-counting classical communication, these approaches can now be seriously considered for quantum networks. The main driver is would be the deduction of optical power in neighbouring DWDM channels, which ultimately lowers the Raman scattered photons into the quantum channel \cite{EraerdsRaman}
{Calculate reduction in power from state of the art SFP modules}

@@

\begin{itemize}
\tightlist
\item
  Efficiency = 0.84
\item
  Afterpulsing = 0 \%
\item
  Jitter = 15 ps
\item
  Deadtime = 30 ns {measure 3dB flux}
\item
  Area = 330 \(\mu m^2\)
\item
  Dark count rate = 20~Hz
\end{itemize}

@@

In the future, the performance of the optical communication system could be improved by using, high count rate SNSPD arrays. Recently published high-count rate arrays have figures of merit of {\(FoM_T\) for Peacoq and Resta2023 results}. This would result in a proportinal increase in the data rate.
{\(FoM_T\) for fastest InGaAs/InP gated detector}
These devices are ideal for fiber-based optical communication. In free-space, the active area is especially important, whithout the use of an adaptive optics system.
{\(FoM_T\) for DSOC array}
